%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvpresentations}

%---------------------------------------------------------
\cvpresentation %Telluride
{\textbf{Beck, R.A.}; Li, X., \textit{Computational Study of Nanodiamond Defects Influencing Experimental Design}. (Oral Presentation) Nanomaterials: Computation, Theory, Machine Learning and Experiment}
{Telluride, CO} % Location
{June 2023} % Date(s)

%---------------------------------------------------------
\cvpresentation %IRG2
{\textbf{Beck, R.A.}; Sushko, P.; Xu, X; Li, X., \textit{Investigation of Chromium Iodide Skyrmionic Structures}. (Oral Presentation) Materials Research Science and Engineering Center.}
{University of Washington} % Location
{Aug. 2020} % Date(s)

%\cvpresentation %IRG2
%{\textbf{Beck, R.A.}; Huang, Y.; Ganas, A.; Pauzauskie, P.; Xu, X; Li, X., \textit{Noble Gas Incorporation into Nanodiamond}. (Oral Presentation) Materials Research Science and Engineering Center.}
%{University of Washington} % Location
%{Aug. 2020} % Date(s)

%---------------------------------------------------------
\cvpresentation %IRG2
{\textbf{Beck, R.A.}; Sun, S.; Liu, H.; Li, X., \textit{Investigation of Layered Chromium Iodide Structures}. (Oral Presentation) Materials Research Science and Engineering Center.}
{University of Washington} % Location
{Oct. 2019} % Date(s)


%---------------------------------------------------------
\cvpresentation %ESQC
{\textbf{Beck, R.A.}; Lu, L.; Petrone, A.; Ong, A.C.; Pauzauskie, P.; Li, X., \textit{Spectroscopic Signatures of the Nitrogen B and H\textsubscript{4} Aggregates in Nanodiamonds}. (Poster) European Summerschool in Quantum Chemistry.}
{Sicily, Italy} % Location
{Sept. 2019} % Date(s)


%---------------------------------------------------------
\cvpresentation %NWTCCCCC
{\textbf{Beck, R.A.}; Sun, S.; Liu, H.; Li, X., \textit{Investigation of Magnetic Properties of a Two-Dimensional Chromium Iodide Material}. (Oral Presentation) Northwest Theoretical Chemistry Conference.}
{Pullman, WA} % Location
{June 2019} % Date(s)


%---------------------------------------------------------
\cvpresentation %IRG1 scnd time
{\textbf{Beck, R.A.}; Petrone, A.; Li, X., \textit{Examination of Spectroscopic Signatures of Nanodiamond Defects}. (Oral Presentation) Materials Research Science and Engineering Center.}
{University of Washington} % Location
{Sept. 2018} % Date(s)


%---------------------------------------------------------
\cvpresentation
{\textbf{Beck, R.A.}; Petrone, A.; Li, X., \textit{Spectroscopic Response to the Loss of Nanodiamond Surface Crystallinity}. (Poster) Northwest Theoretical Chemistry Conference}
{Richland, WA} % Location
{Oct. 2017} % Date(s)


%---------------------------------------------------------
\cvpresentation
{\textbf{Beck, R.A.}; Petrone, A.; Li, X., \textit{Spectroscopic Signatures of Surface Reconstructions of Nanodiamond}. (Oral Presentation) Materials Research Science and Engineering Center.}
{University of Washington} % Location
{Oct. 2017} % Date(s)


%---------------------------------------------------------
%\cvpresentation
%{Petrone, A.; Williams-Young, D.B.; \textbf{Beck, R.A.}; Li, X., \textit{Surface Reorganization and X-ray Spectra of Nitrogen-Vacancy Containing Nanodiamonds}. (Oral Presentation) 254\textsuperscript{th} ACS National Meeting}
%{Washington D.C.} % Location
%{Aug. 2017} % Date(s)


%---------------------------------------------------------
\cvpresentation
{Esmeralda, L.; \textbf{Beck, R.A.}; Halligan, K., \textit{Crosslinking of the Antibody Anti-Human IL-13R Alpha 2 Peptide IgY to FITC via PDPH}. (Poster) 251\textsuperscript{st} ACS National Meeting}
{San Diego, CA} % Location
{Mar. 2016} % Date(s)


%---------------------------------------------------------
\end{cvpresentations}

